(Working Title) Stellar and Planetary Properties of \KT\ \Ci\ Candidates and Validation of \Nvalidated\ Systems, (Including a Planet Receiving Earth-like Insolation?)

### 2015-03-07 ms.tex
fixing and adding some affiliations

\author{
% The Heavy Lifters
Benjamin T. Montet\altaffilmark{1,2}, 
Daniel Foreman-Mackey\altaffilmark{3},
Timothy D. Morton\altaffilmark{4},
% The Benefactors
John Asher Johnson,
David W. Hogg,
% The Observers
% (ranked by integration time x collecting area)
Brendan P. Bowler,
David W. Latham,
Allyson Bieryla,
Andrew W. Mann,
And Any TRES Team Members We Should Add
}

\email{btm@astro.caltech.edu}

\altaffiltext{1}{Cahill Center for Astronomy and Astrophysics, California Institute of Technology, 1200 E. California Blvd., MC 249-17, Pasadena, CA 91106, USA}
\altaffiltext{2}{Harvard-Smithsonian Center for Astrophysics, 60 Garden
Street, Cambridge, MA 02138, USA}
\altaffiltext{3}{Department of Astronomy, University of Michigan, Ann Arbor, MI 48109, USA}
\altaffiltext{4}{Department of Astrophysics, 4 Ivy Lane, Princeton University, Princeton, NJ 08544, USA}

>>>>

\newcommand{\caltech}{2}
\newcommand{\cfa}{3}
\newcommand{\nyu}{4}
\newcommand{\princeton}{5}
\newcommand{\mpia}{6}
\newcommand{\cds}{7}
\author{%
% The Heavy Lifters
Benjamin~T.~Montet\altaffilmark{1,\caltech,\cfa},
Daniel~Foreman-Mackey\altaffilmark{\nyu},
Timothy~D.~Morton\altaffilmark{\princeton},
% The Benefactors
John~Asher~Johnson\altaffilmark{\cfa},
David~W.~Hogg\altaffilmark{\nyu,\mpia,\cds},
% The Observers
% (ranked by integration time x collecting area)
Brendan~P.~Bowler,
David~W.~Latham,
Allyson~Bieryla,
Andrew~W.~Mann,
And Any TRES Team Members We Should Add
}

\altaffiltext{1}         {btm@astro.caltech.edu}
\altaffiltext{\caltech}  {Cahill Center for Astronomy and Astrophysics,
                          California Institute of Technology, Pasadena, CA,
                          91125, USA}
\altaffiltext{\cfa}      {Harvard-Smithsonian Center for Astrophysics,
                          Cambridge, MA 02138, USA}
\altaffiltext{\nyu}      {Center for Cosmology and Particle Physics,
                          Department of Physics, New York University,
                          4 Washington Place, New York, NY, 10003, USA}
\altaffiltext{\princeton}{Department of Astrophysics, Princeton University,
                          Princeton, NJ, 08544, USA}
\altaffiltext{\mpia}     {Max-Planck-Institut f\"ur Astronomie,
                          K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\altaffiltext{\cds}      {Center for Data Science,
                          New York University,
                          726 Broadway, 7th Floor, New York, NY, 10003, USA}
